Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2015-04-14 response.txt

* In the abstract, it is said "We investigate whether or not the
distributions resemble uniform foreground screens, as commonly
assumed.". I see several issues with this statement. First of all, the
word "uniform" is ambiguous. Later in the paper it appears to probably
mean that it implies there is no differential reddening between the gas
and the stars. At this point it is not clear in my opinion. The terms
used in the paper really need to be properly and strictly defined. As it
is, the paper appears somewhat vague, partly because of that I think.
Also, "foreground screens" are not commonly assumed. I would go as far
as saying they besides a handful of specific cases and academic
exercises, they are nearly never assumed for practical proposes on
entire galaxies. I believe we have known since the IRAS days that a
foreground screen cannot be a good assumption in general for entire
galaxies as this would yield very low dust masses that are not at all in
line with the estimate from IR observations. And for sure it has fallen
even more into disuse since the Calzetti+94 paper and the subsequent
Charlot & Fall+00 model.

We clarify our language in the last paragraph of the Introduction. 
Foreground screens are commonly assumed by the high-redshift community;
we expand our explanation in the Introduction.

* Still on the vocabulary, I do not think it is defined anywhere what
"dust-poor" and "dusty" galaxies are. This sort of thing contributes to
the vagueness of the paper. The reader does not know what she is really
looking it. A more quantitative description of the two samples would be
especially useful. Directly related to this point, another important
issue I have is the very unclear selection of the sample. I do not think
the reader would understand why these sample specifically were selected.

We clarify our language in the last paragraph on the Introduction.  The
sample of low-redshift dust-poor galaxies is included to show that we
can reproduce the Calzetti result; the samples of dusty galaxies are
included because we know little about their dust distributions.

* "We often assume that dust grains are distributed as a uniformly thick
screen between us and the galaxy's stars and gas (Calzetti et al.
1994).". I do not see where Calzetti would have stated that. What they
say in the abstract is "The data from the 39 galaxies are compared with
five models for the geometrical distribution of dust, adopting as
extinction laws both the Milky Way and the Large Magellanic Cloud laws.
The commonly used uniform dust screen is included among the models. We
find that none of the five models is in satisfactory agreement with the
models". What the authors perhaps mean is that 20 years ago some people
still considered an uniform dust screen as an acceptable model. I think
this time is long gone, even though it is sometimes referred to as a
standard comparison point as it has a very simple link with the optical
depth.

The abstract has only a small fraction of the content of the paper. 
Calzetti et al. 1994 has an extended discussion of the uniform screen
model in sections 5.1 and 6.2.  We clarify our discussion of the uniform
screen model in the Introduction.

* "If a dusty galaxy's measured Halpha attenuation agreed with the
prediction from the Calzetti+00 attenuation formula, we might conclude
that the galaxy has a uniform dust distribution only if we believe that
the prediction is valid". I think that this statement is not correct.
First of all, the starburst curve is purely observational. No assumption
whatsoever on the geometry was made. However, it can be explained by
certain geometries, such as for instance the one described in the
Charlot & Fall 2000 model. Perhaps this is what the authors mean?

We clarify our discussion of the uniform screen model in the
Introduction. k(lambda) is an empirical equation; predictions of
attenuation values from k(lambda) do assume a dust distribution.

* First paragraph of Sect. 2.2.3. The K98 IR estimator actually assumes
that the galaxy is totally buried into dust. Therefore, combining the UV
with the TIR directly can be a dangerous game (though quite common in
the literature). As UV is detected, galaxies are not that strongly
attenuated so the assumption does not hold and the dust heating sources
are not the same anymore, which in turn should change the calibration
coefficient. Also, the listed assumptions are not enough in my opinion.
Even if the SFR is constant over 10^8 years, the Halpha and UV+IR SFR
would not be the same, because of contamination by stars older than 100
Myr in the UV but not in Halpha. As possible biases in the derivation of
the SFR would have a direct impact on the results, I suggest that they
are fully taken into account and properly discussed in the paper. In any
case, beyond that, assuming in effect that SFR(Halpha)=SFR(UV+TIR) is a
very strong assumption. If there is a tiny wiggle of the SFR in the last
few Myr, that is sufficient to throw the different SFR completely off
from one another. As said just above, the results of this paper are
sensitive to such effects. I think it is therefore especially important
that the impact of such variations is discussed in more detail than in a
lone paragraph in Section 4.

* In section 3, I find very odd to present the results in terms of
escape fraction, rather than attenuation as is customary. While
technically they are equivalent quantities, I find that using escape
fractions is detrimental to the clarity of the paper. I would strongly
suggest to switch to attenuations.

We disagree.

* Section 3.1. I understand what the authors are trying to do, that is
testing their method. Which is a very good thing of course. That being
said, I cannot help but wonder whether the results are really meaningful
here. If I remember correctly, there is quite a bit of scatter for this
sample around the IRX-beta relation. What if this scatter is driven by a
combination of variations in the attenuation curves and variations in
the age of UV-emitting stellar populations? I think a perhaps more
convincing test would be to create a mock catalog of galaxies and apply
that method on it to see whether it can recover the proper parameters.
As an added bonus, it would be trivial to test whether a variation of
the SFH (for instance including a recent burst of star formation). I
think that would be a very convincing test that the proposed method is
indeed providing good results. Actually at this point I am also a bit
confused regarding beta. Its computation is described earlier in the
paper but I do not see it used in practice.

We are interested in reproducing the literature relation for a sample of
dust-poor galaxies similar to the one studied by Calzetti.  The test
proposed here is for reproducing the relation assumed by a model.  We do
not know what the "true" values are for the Lyman break analogs or the
Calzetti sample.  So while we might be able to say that we reproduce the
relation assumed by the model, we would not be able to say that the mock
galaxies reproduce real galaxies.

We use beta only to obtain rest-frame UV luminosities at a common
wavelength.

* Beginning of Section 4. There is more than just the assumption that
dusty galaxies follow the starburst law. There is also the assumption
that all galaxies in a given sample have the same intrinsic UV color I
think. It is not clear at all to me whether that is actually the case.

* Last paragraph of the conclusion. I doubt ALMA will be used to provide
direct test of the "uniform screen assumption". Not that it cannot, but
rather this assumption is known to be invalid for most practical
purposes. There is an enormous quantity of archival observations
available for numerous instruments showing the beautifully complex
interplay between stars and dust in the Milky and in nearby galaxies.

We clarify that ALMA will be a boon to high-redshift galaxies.

* Finally, some general comments. The differential reddening is not
mentioned in the paper even though that is what the authors aim at
studying. In her last attenuation law papers, Calzetti defines the
difference of the attenuation between the stars and the gas in terms of
differential reddening rather than in terms of escape ratios (that is,
E(B-V)stars=0.44*E(B-V)gas rather than AVstars=0.44*AVgas). This is an
important difference as Rv is different between the starburst law
(Rv=4.05) and the Milky Way law (Rv=3.1). If I remember correctly, that
can make a noticeable difference when computing A(Halpha)/A(FUV).

We hope our language clarifies this point.  We are only interested in
the differential reddening if we believe the Calzetti formula applies to
high-redshift dusty galaxies.  When we discuss whether high-redshift
galaxies obey or disobey the Calzetti attenuation formula, we include Rv
in our definition of the attenuation formula, k(lambda). (In short, we
do not aim to study the differential reddening.)

Some comments on more minor points follow.

* There are sentences between parentheses in the middle of the text. It
disturbs the reading flow in my opinion. I would suggest to either add
them as footnotes and to integrate them fully in the rest of the text.

* Please provide a reference for Willman 1. I assume many readers will
be ignorant of the details of this object, so information should be made
easy to access for those who are curious to know more about it.

* "The arrangement of dust is often described, oddly, as its geometry".
I am not sure what is particularly odd in that. But more precisely, what
is described is the relative arrangement of dust relative to stars as
this is one of the major parameters that govern the actual impact of
dust on the emerging radiation.

* "If we want to learn about galaxies, morphology should be a
wavelength-independent word". Should it? I do not see why. The
differences in morphologies in different bands are extremely informative
on the physics of galaxies.

* "An attenuation formula is denoted k(lambda) or k'(lambda)." I do not
think this statement is useful here. First the term "attenuation
formula" is extremely vague. Then, unless I am mistaken, k is not used
in any meaningful way elsewhere in the paper anyway.

* "A low-redshift galaxy [...] underestimates the measured Halpha
attenuation." Please back this with a reference.

* "Liu+13 find that the dust distribution around ionizing stars
throughout M83 is clumpy at a spatial scale of 6 pc." Unless I am
mistaken, this is not at all what they say. Quoting their abstract
"[...] we conclude that a large diversity of absorber/emitter geometric
configurations can account for the data, implying a more complex
physical structure than the classical foreground screen assumption". The
article barely mentions at all the clumpy distribution.

* "If we choose to think of dust distributions as clumpy [...] 60% of
the number of clumps surrounding ionizing stars (Calzetti+97a)". Once
again, I do not see where the mentioned paper cites that number. If it
is indeed that paper: http://de.arxiv.org/abs/astro-ph/9706121 then the
word clump is not even mentioned even once in the paper. Please clarify
this part.

* "if we consider that galaxies have centers and outskirts." That
statement is odd. Any spatially bounded object has outskirts.

* Price+13 should be Price+14.

* About the correction for the NII contamination, which should be
metallicity dependent, what about using a mass-metallicity relation for
instance? That would be far from perfect but certainly better than
assuming a constant [NII]/Halpha.

* Editorial question, it looks odd that the second author of the paper
is cited for data provided as "private communication".

* Sect. 2.2.1, second paragraph. Maybe I am misunderstanding what is
written, but it appears to say that fitting the CE01 templates on the 24
micron band only will overestimate the 70 and 100 micron fluxes (and
therefore most likely it will also overestimate the TIR), and that the
TIR found in the paper is even higher. If it is the case, I find that
very worrisome. If it is not the case, please clarify this paragraph to
remove ambiguities.

* The TIR luminosities of the so-called dust-poor and dusty galaxies are
not that different. This suggests some possible selection effects. This
aspect should be discussed in detail in the paper.

* The title of Sect. 3.1 is unclear. One would wonder what "relation" is
considered here.

* Sect. 3.1, it would be useful to specify what exactly is the "low
redshift IRX-beta relation".

* Last paragraph of Sect. 4. This assumes that the stars and the gas
follow the same attenuation law. This may or may not be the case.
Calzetti considers that this is not the case. Also later in that
paragraph, I may be missing something, but I do not understand why this
would prove that SFH are correct. Just after the authors rightly mention
that f(Halpha)/f(Hbeta) is SFH-independent. So this test just does not
tell us much of anything regarding the SFH I think. Please clarify.

As a final note, here is the assessment by a statistical expert on the
fitting done in the paper: The choice of regression methodology in Fig 4
is unclear to me. Why do the orange lines seem constrained to pass
through the origin? The resulting fit for the top right diagram, for
example, is clearly poor. Statisticians would recommend that, when
heuristic (e.g. linear) parametric models fit poorly, that nonparametric
local regression methods be used to show the true behavior of the
bivariate relationship. There are various methods -- splines, LOESS,
kriging (= Gaussian process regression) -- some of which give local
confidence bands. Several recent texts are available; e.g. K.Takezawa
`Introduction to Nonparametric Regression'. For implementation in the
public R statistical software environment, see a tutorial on density
estimation at http://www2.astro.psu.edu/users/edf/Caltech_2014.

### 2015-04-14 paper.tex
Updates

\begin{abstract}
Do spatial distributions of dust grains in galaxies have typical forms, as do
spatial distributions of stars?  We investigate whether or not the distributions
resemble
uniform foreground screens, as commonly assumed.  We use rest-frame infrared,
ultraviolet, and H$\alpha$ line luminosities of dust-poor and dusty galaxies
at $z \sim 0$ and $z \sim 1$ to compare measured H$\alpha$ escape fractions
with those predicted by the Calzetti attenuation formula.  The predictions,
based on
UV escape fractions, overestimate the measured H$\alpha$ escape fractions for
all samples.  The
interpretation of this result for dust-poor $z \sim 0$ galaxies is that regions
with ionizing stars have more dust than regions with nonionizing UV-emitting
stars.  Dust distributions for these galaxies are nonuniform.  The
interpretation of the overestimates for dusty galaxies at both redshifts is
less clear.  If the attenuation formula is inapplicable to these galaxies,
perhaps the disagreements are unphysical; perhaps dust distributions in
these galaxies are uniform.  If the attenuation formula does apply, then dusty
galaxies have nonuniform dust distributions; the distributions are more
uniform than they are in dust-poor galaxies.  A broad range of H$\alpha$ escape
fractions at a given UV escape fraction for $z \sim 1$ dusty galaxies, if real,
indicates diverse dust morphologies and the implausibility of the screen
assumption.
\end{abstract}

@@

Dust attenuates a galaxy's intrinsic luminosity at ultraviolet (UV) and optical
wavelengths.  We often assume that dust grains
are distributed as a uniformly thick screen between us and the galaxy's stars
and gas \citep{calzetti94}.  From the uniform screen assumption follows an
attenuation
formula that depends solely on wavelength; intrinsic luminosity is recovered
from emergent luminosity and attenuation calculated from the formula.

An attenuation formula is denoted $k(\lambda)$ or $k'(\lambda)$.  It differs
from an extinction formula, which is independent of the spatial distribution
of dust.  When we derive an extinction formula, it is valid for the small area
surrounding a star in the Milky Way, not the large area containing a mix of
stars and gas in distant galaxies.  In an illustrative sense an attenuation
formula is an extinction formula convolved with a spatial distribution of dust.

@@

%This paper is organized as follows.  We present the data and derived quantities
%in \S\ref{sec:data}.  The relation is in \S\ref{sec:results}.  Our argument is
%in \S\ref{sec:discuss}.  We conclude in \S\ref{sec:conclude}.
For this paper we assume a cosmology with $H_{0} = 70$ km s$^{-1}$ Mpc $^{-1}$,
$\Omega_{\mathrm{m}} = 0.3$, and $\Omega_{\Lambda} = 0.7$.

@@

ALMA is beginning to produce images of the dust distributions in galaxies.
These images lead to direct tests, independent of the attenuation formula, of
the uniform screen assumption.  They also have the potential to reveal the
parts of galaxies that may never be detected at UV and optical wavelengths:
surprises surely abound.

>>>>

\begin{abstract}
Do spatial distributions of dust grains in galaxies have typical forms, as do
spatial distributions of stars?  We investigate whether or not the distributions
resemble
uniform foreground screens, as commonly assumed by the high-redshift galaxy
community.  We use rest-frame infrared,
ultraviolet, and H$\alpha$ line luminosities of dust-poor and dusty galaxies
at $z \sim 0$ and $z \sim 1$ to compare measured H$\alpha$ escape fractions
with those predicted by the Calzetti attenuation formula.  The predictions,
based on
UV escape fractions, overestimate the measured H$\alpha$ escape fractions for
all samples.  The
interpretation of this result for dust-poor $z \sim 0$ galaxies is that regions
with ionizing stars have more dust than regions with nonionizing UV-emitting
stars.  Dust distributions for these galaxies are nonuniform.  The
interpretation of the overestimates for dusty galaxies at both redshifts is
less clear.  If the attenuation formula is inapplicable to these galaxies,
perhaps the disagreements are unphysical; perhaps dust distributions in
these galaxies are uniform.  If the attenuation formula does apply, then dusty
galaxies have nonuniform dust distributions; the distributions are more
uniform than they are in dust-poor galaxies.  A broad range of H$\alpha$ escape
fractions at a given UV escape fraction for $z \sim 1$ dusty galaxies, if real,
indicates diverse dust morphologies and the implausibility of the screen
assumption.
\end{abstract}

@@

Dust attenuates a galaxy's intrinsic luminosity at ultraviolet (UV) and optical
wavelengths.  To recover an intrinsic luminosity from an emergent luminosity we
often assume that dust grains
are distributed as a uniformly thick screen between us and the galaxy's stars
\citep{calzetti94}.  From the uniform screen assumption follows an
attenuation formula that depends solely on wavelength.

An attenuation formula is denoted $k(\lambda)$ or $k'(\lambda)$.  It differs
from an extinction formula, which is independent of the spatial distribution
of dust.  When we derive an extinction formula, it is valid for the small area
surrounding a star in the Milky Way, not the large area containing a mixture of
stars in distant galaxies.

If we write an equation like this:

\begin{math}
L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}} = 10^{-\mathrm{A}/2.5} = 10^{-\mathrm{E(B-V)} k(\lambda)/2.5}
\end{math}

we assume a uniform screen not because $k(\lambda)$ is solely dependent on
wavelength, but because $L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}}$ is solely
dependent on
wavelength.  In an illustrative sense
$L_{\mathrm{emergent}}/L_{\mathrm{intrinsic}}$
is an attenuation formula convolved with a spatial distribution of dust.

@@

%This paper is organized as follows.  We present the data and derived quantities
%in \S\ref{sec:data}.  The relation is in \S\ref{sec:results}.  Our argument is
%in \S\ref{sec:discuss}.  We conclude in \S\ref{sec:conclude}.
For this paper we assume a cosmology with $H_{0} = 70$ km s$^{-1}$ Mpc $^{-1}$,
$\Omega_{\mathrm{m}} = 0.3$, and $\Omega_{\Lambda} = 0.7$.  Our terminology
is: (1) a \emph{uniform} screen is a screen equally thick between a region with
stars which ionize gas and a region with stars which emit in the UV and do not
ionize gas; (2) a \emph{dust-poor} galaxy is selected from a UV image and
generally has low values of UV and H$\alpha$ attenuation; and (3) a \emph{dusty}
galaxy is selected from an IR image and generally has high values of UV and
H$\alpha$ attenuation.  The samples of dust-poor and dusty galaxies are not
dichotomous.  More details are in the following section.

@@

ALMA is beginning to produce images of the dust distributions in high-redshift
galaxies.  These images lead to direct tests, independent of the attenuation
formula, of the uniform screen assumption.  They also have the potential to
reveal the parts of galaxies that may never be detected at UV and optical
wavelengths: surprises surely abound.
